A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-22 src/tex/ms.tex

Adopting a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$, the yield set $y/Z_\odot=1$ corresponds to an integrated SN Ia rate of $N_{\rm Ia}/M_\star=\num{1.37e-3}$ M$_\odot^{-1}$, and the higher set $y/Z_\odot=3$ corresponds to $N_{\rm Ia}/M_\star=\num{5.36e-3}$ M$_\odot^{-1}$

>>>>

Adopting a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$, the yield set $y/Z_\odot=1$ corresponds to an integrated SN Ia rate of $N_{\rm Ia}/M_\star=\num{1.79e-3}$ M$_\odot^{-1}$, and the higher set $y/Z_\odot=3$ corresponds to $N_{\rm Ia}/M_\star=\num{4.1e-3}$ M$_\odot^{-1}$.
